Untitled CAV Paper

### 2016-01-17 paper.tex
Added a section on abstract game trees

A set of runs for a bounded game of rank $n$ can be represented by a \emph{game
tree} of depth $n$ with states in the nodes and labels as edges. A
\emph{strategy tree} similarly represents a strategy by restricting the edges
in a game tree to obey $\pi^c$ for a controller strategy or $\pi^e$ for an
environment strategy.

@@

The bounded synthesis algorithm from \cite{nina} constructs abstractions of the
game in the form of \emph{abstract game trees}.

>>>>

@@

A set of runs can be symbolically represented by a tree of labels. Each edge of
the tree is either a \emph{fixed} valuation of controllable or uncontrollable
variables, or it is \emph{unfixed} denoting any values are possible. Also, the
tree must alternate between controllable and uncontrollable edges to reflect
the alternating turns of the game. The entire set of runs of a bounded game of
rank $n$ is symbolically represented by a tree of depth $2n$ and width 1
populated by unfixed edges. Reducing the set of runs in a game forms an
abstract game, which can be represented symbolically by an \emph{abstract game
tree}.

A strategy is equivalent to the set of all runs with the player's labels
obeying the strategy mapping $\pi$. Therefore, a strategy can also be
represented by a tree. Relaxing the restriction of the strategy mapping allows
for a \emph{partial strategy} in which multiple labels are now possible for a
single state.

A strategy or partial strategy can also be thought of as an abstract game. A
partial strategy for the controller is a restriction only on the controllable
labels in the game. So if the environment can not win in the abstract game
equivalent to the controller's partial strategy, then all strategies allowable
by that partial strategy must be winning.
